---
title: "SupercalifragilsticexpiDataScience"
author: "Tom Yoder - MIS 5470"
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---


Using Data Science to Create Disney Magic - Data Exploration   
============================================================

What exactly did Touring Plans give us? Let's load four of my favorite rides.
------
```{r Load Data}
SpaceshipEarth <- read.table(file= "Data/spaceship_earth.csv", header=TRUE, sep=",")

Pirates <- read.table(file= "Data/pirates_of_caribbean.csv", header=TRUE, sep=",")

SplashMountain <- read.table(file= "Data/splash_mountain.csv", header=TRUE, sep=",")

ToyStory <- read.table(file= "Data/toy_story_mania.csv", header=TRUE, sep=",")

MetaData <- read.csv(file= "Data/metadata.csv")

```

That took a little bit, let's see what these data sets look like. 

```{r Preview Data}
head(SpaceshipEarth)
```

For each ride we get the data of the observation, time, posted wait time (SPOSTMIN) and actual wait time (SACTMIN).
Checking out the structure of Spaceship Earth, it looks like we have 240919 observations over 2422 different dates.

```{r Structure of Spaceship Earth}
str(SpaceshipEarth)
```

Let's see if every ride has the same number of dates.

```{r Structure of Pirates of the Caribbean}
str(Pirates)
```

More observations for Pirates than Spaceship Earth on less dates. That would've been too easy anyways.

What fields do we have in the Metadata file?

```{r Structure of Metadata}
str(MetaData)
```

That is a lot of metadata! I will study the data dictionary and let you know what is what as we use it. 

For now let's put together a subset of data for Spaceship Earth using only the year 2017.

